Cover Letter

### 2021-11-17 paper/latex/PMB/cover_letter.tex
setup for PMB

\documentclass[10pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{csquotes}
\usepackage[british]{babel}
\usepackage{url}
\usepackage{graphicx}
\graphicspath{ {figs/} }
\usepackage{geometry}
\usepackage{amsmath}
\usepackage{graphicx}
% \usepackage[square,numbers]{natbib}
\usepackage[
    backend=biber,
    style=authoryear,
    natbib=true,
    sortlocale=en_US,
    url=false,
    doi=true,
    eprint=false
]{biblatex}
\addbibresource{cover.bib}
\usepackage{fancyhdr}
\usepackage{color}
\definecolor{darkblue}{rgb}{0.,0.,0.4}
\definecolor{darkred}{rgb}{0.5,0.,0.}
\usepackage[pdftex,colorlinks=true,linkcolor=darkblue,citecolor=darkred,urlcolor=blue]{hyperref}

@@

\noindent
\today, \\
To the Many Editors of Network Neuroscience, \\

We hope you will consider our manuscript \emph{Random Matrix Theory Tools for the Analysis of
Functional Magnetic Resonance Imaging Examinations} for publication in Network Neuroscience as a
\emph{Research} article. In it, we apply mathematical tools from random matrix theory (RMT) to
analyze a wide variety of functional magnetic resonance imaging (fMRI) data, and release
open-source software \citep{bergerStfxecutablesEmpyricalRMTPreliminary2020} to facilitate such analyses with a wider variety of data beyond fMRI.

@@

\footnotesize
\AtNextBibliography{\footnotesize}
\printbibliography[heading=none]

>>>>

\documentclass[10pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{csquotes}
\usepackage[british]{babel}
\usepackage{url}
\usepackage{graphicx}
\graphicspath{ {figs/} }
\usepackage{geometry}
\usepackage{amsmath}
\usepackage{graphicx}
% \usepackage[square,numbers]{natbib}
\usepackage[
    backend=biber,
    style=authoryear,
    natbib=true,
    sortlocale=en_US,
    url=false,
    doi=true,
    eprint=false
]{biblatex}
\addbibresource{cover.bib}
\usepackage{fancyhdr}
\usepackage{color}
\definecolor{darkblue}{rgb}{0.,0.,0.4}
\definecolor{darkred}{rgb}{0.5,0.,0.}
\usepackage[pdftex,colorlinks=true,linkcolor=darkblue,citecolor=darkred,urlcolor=blue]{hyperref}

@@

\noindent
\today, \\
To the Editors of Network Neuroscience, \\

We hope you will consider our manuscript \emph{Random Matrix Theory Tools for the Analysis of
Functional Magnetic Resonance Imaging Examinations} for publication in Network Neuroscience as a
\emph{Research} article. In it, we apply mathematical tools from random matrix theory (RMT) to
analyze a wide variety of functional magnetic resonance imaging (fMRI) data, and release
open-source software \citep{bergerStfxecutablesEmpyricalRMTPreliminary2020} to facilitate such analyses with a wide variety of data.

@@

\footnotesize
\begin{center}
\noindent\rule{6cm}{0.4pt}
\end{center}

\AtNextBibliography{\footnotesize}
\printbibliography[heading=none]
